---
title: "`r params$title`"
author: "`r params$org`"
date: "`r params$date`"
output:
  pdf_document:
    latex_engine: xelatex
  word_document: default
  html_document:
    df_print: paged
geometry: a4paper, margin=2.5cm
mainfont: Calibri
fontsize: 10pt
params:
  title: Smart Metering Data - Energy Report
  author: Issy Middleton
---
```{r setup, include=FALSE}
# Knitr setup
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```
```{r include=FALSE}
# Load project
library("ProjectTemplate")
load.project()
# Run code in analysis.R script)
source("src/eda-Consumption.R")
```
This report provides the findings of exploratory analysis undertaken using half-hourly consumption data from `r format(min(consumption$date), format = "%d %B %Y")` to `r format(max(consumption$date), format = "%d %B %Y")`, `r days` days. 

Electricity demand varies significantly when measured each half hour. The pattern below shows peaks and troughs for daily and weekly patterns of usage. The lowest half hourly reading recorded during the period was `r (min(consumption$kWh))` kWh. The average half hourly reading recorded during the period was `r round(mean(consumption$kWh),digits = 2)` kWh. Total consumption during this time period was `r format(round(sum(consumption$kWh), digits = 0))` kWh, equating to a daily average of `r format(round(sum(consumption$kWh)/days), digits = 1)` kWh. 

### Half Hourly Demand Profile
```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
HHLine
```
\newpage

### Daily Electricity Usage 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
DailyLine
```

### Average Half-Hourly Demand Profile by Typical Day 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
DailyProfile
```

### Heatmap

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
heatmap
```

### Density Plot showing seasonal variation

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
Density
```


### Hourly Demand Profile by Week - 2022 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
Hourbyweek2022
```

### Weekly Electricity Consumption by Time of Day - 2022

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
WeekYearToD2022
```

### Time of Day Electricity Usage (4 hour periods combined) - 2022

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
HHLine4Hours2022
```

### Hourly Demand Profile by Week - 2023

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
Hourbyweek2023
```

### Weekly Electricity Consumption by Time of Day - 2023

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
WeekYearToD2023
```

### Time of Day Electricity Usage (4 hour periods combined) - 2023

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
HHLine4Hours2023
```

\newpage

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
kable(Peak, align = "lcccc", booktabs = TRUE, caption = "Peak Four-Hourly Periods") %>%
  row_spec(0, bold = TRUE)%>%
  kable_styling(latex_options = "striped")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
kable(Stats_b, align = "lcccc", booktabs = TRUE, caption = "Peak Half-Hourly Periods") %>%
  row_spec(0, bold = TRUE) %>%
  kable_styling(latex_options = "striped")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
kbl(Cons_Year2022, booktabs = TRUE, caption = "Weekly Consumption - 2022") %>%
kable_styling(font_size = 8,latex_options = "striped")
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Insert consumption graphs plots
kbl(Cons_Year2023, booktabs = TRUE, caption = "Weekly Consumption - 2023") %>%
kable_styling(font_size = 8,latex_options = "striped")
```
